---
title: R Colors in CSS
output: 
  html_document:
    css: r-colors.css
---

```{r clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

```{css echo=FALSE}
.background {
  display: inline-block;
  height: 30px;
  width: 10vw;
  cursor: pointer;
}
.foreground {
  cursor: pointer;
}
#demo-text {
	padding: 1em 2em 2em 2em;
	position: sticky;
	top: 0;
	z-index: 999;
	margin-bottom: 1em;
}
#demo-text p { font-size: 1.5em; }

#demo-text {
  transition: all 150ms linear;
}

#demo-text .mono { 
  font-size: 0.8em;
  font-family: monospace; 
}

.darkmode {
  background-color: #333;
  color: #FFF;
}
#toggle-dark-mode {
  position: fixed;
  bottom: 32px;
  right: 32px;
  width: 32px;
  height: 32px;
  border-radius: 50%;
  background-color: black;
  cursor: pointer;
  line-height: 32px;
  z-index: 9999;
}
#toggle-dark-mode::before {
  display: table-cell;
  vertical-align: middle;
  height: 32px;
  width: 32px;
  text-align: center;
  line-height: normal;
}
.darkmode #toggle-dark-mode {
  background-color: white;
}
#toggle-dark-mode::before {
  content: '\1F319';
}
.darkmode #toggle-dark-mode::before {
  content: '\2600\FE0F';
}
.darkmode .ReactTable {
	background-color: #333;
}
```

> All of R's [named colors](https://rdrr.io/r/grDevices/colors.html)
> in [one CSS stylesheet](r-colors.css).


```{r child="usage.Rmd"}
```


## Colors

<div id="demo-text" class="bg-white black"><h2>Preview</h2><p>Click on a color below<p></div>

::: {.table-responsive} :::

```{r echo=FALSE}
library(glue)
x <- data.frame(
  name = glue('<span class="foreground {colors()}">{colors()}</span>'),
  color = glue('<span class="background bg-{colors()}"></span>'),
  foreground = glue(".{colors()}"),
  background = glue(".bg-{colors()}")
)
```

```{r echo=FALSE}
reactable::reactable(
  data = x,
  sortable = TRUE,
  searchable = TRUE,
  pagination = FALSE,
  highlight = TRUE,
  columns = list(
    name = reactable::colDef("Name", html = TRUE),
    color = reactable::colDef("Color", html = TRUE),
    foreground = reactable::colDef("Foreground Class"),
    background = reactable::colDef("Background Class")
  ),
  onClick = reactable::JS("
    function(rowInfo, colInfo) {
      if (!['name', 'color'].includes(colInfo.id)) return
      
      const preview = document.getElementById('demo-text')
      
      const classCell = colInfo.id === 'name' ? 'foreground' : 'background'
      let fg = [...preview.classList].filter(x => !/^bg-/.test(x))
      let bg = [...preview.classList].filter(x => /^bg-/.test(x))
      
      if (classCell == 'foreground') {
        fg = rowInfo.row.foreground.replace('.', '')
      } else {
        bg = rowInfo.row.background.replace('.', '')
      }
      
      preview.classList = fg + ' ' + bg
      preview.querySelector('p').innerHTML = 
        `The quick brown fox jumps over the lazy dog.<br><br>
        <span class=\"mono\">class=\"${fg} ${bg}\"</span>`
    }
  ")
)
```


:::

<div id="toggle-dark-mode"></div>

```{js, echo=FALSE}
const toggleDarkMode = document.getElementById('toggle-dark-mode')
toggleDarkMode.addEventListener('click', function() {
  document.body.classList.toggle('darkmode')
})
```

<a href="https://github.com/gadenbuie/r-colors-css" class="github-corner" aria-label="View source on GitHub"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:var(--darkorange1); color:#fff; position: fixed; top: 0; border: 0; right: 0; z-index:1001;" aria-hidden="true"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
