---
title: R Colors in CSS
output: 
  html_document: 
    css: [dist/r-colors.css, dist/r-colors.hover.css]
    theme: yeti
---

```{r clipboard, echo=FALSE}
xaringanExtra::use_clipboard()

library(metathis)
meta() %>% 
  meta_social(
    title = "R Colors in CSS",
    description = "R's named colors as CSS styles",
    url = "https://pkg.garricakdenbuie.com/r-colors-css",
    image = "https://pkg.garrickadenbuie.com/r-colors-css/social-card.png",
    og_type = "website",
    og_author = "Garrick Aden-Buie",
    twitter_card_type = "summary_large_image",
    twitter_creator = "@grrrck"
  )
```

```{css echo=FALSE}
body {
  font-size: 18px;
}
pre {
  font-size: 16px;
}
.background {
  display: inline-block;
  height: 30px;
  width: 100%;
  cursor: pointer;
}
.foreground {
  cursor: pointer;
}
.color-picker {
  display: flex;
  flex-direction: column;
  height: 100vh;
}
.h-100 { 
  height: 100%; 
}
.overflow-hidden {
  overflow: hidden;
}
#demo-text {
  padding: 1em 2em 2em 2em;
  position: relative;
  margin-bottom: 1em;
}
#demo-text p { font-size: 1.5em; }
@media screen and (max-width: 768px) {
  #demo-text { font-size: 10px; }
}
#demo-text {
  transition: all 150ms linear;
}
#demo-text .mono { 
  font-size: 0.8em;
  font-family: monospace; 
}
#demo-contrast {
  position: absolute;
  bottom: 0;
  right: 0;
  padding: 1em;
}
#demo-contrast:hover {
  text-decoration: none;
}
.darkmode {
  background-color: #333;
  color: #FFF;
}
#toggle-dark-mode {
  position: fixed;
  bottom: 32px;
  right: 32px;
  width: 32px;
  height: 32px;
  border-radius: 50%;
  background-color: black;
  cursor: pointer;
  line-height: 32px;
  z-index: 9999;
}
#toggle-dark-mode::before {
  display: table-cell;
  vertical-align: middle;
  height: 32px;
  width: 32px;
  text-align: center;
  line-height: normal;
}
.darkmode #toggle-dark-mode {
  background-color: white;
}
#toggle-dark-mode::before {
  content: '\1F319';
}
.darkmode #toggle-dark-mode::before {
  content: '\2600\FE0F';
}
.darkmode .ReactTable {
  background-color: #333;
}
```

```{js, echo=FALSE}
getLuminance = function(r, g, b) {
  r /= 255;
  g /= 255;
  b /= 255;

  let red = r <= 0.03928 ? r / 12.92 : ((r + 0.055) / 1.055) ** 2.4;
  let green = g <= 0.03928 ? g / 12.92 : ((g + 0.055) / 1.055) ** 2.4;
  let blue = b <= 0.03928 ? b / 12.92 : ((b + 0.055) / 1.055) ** 2.4;

  // Compute and return luminance
  return 0.2126 * red + 0.7152 * green + 0.0722 * blue;
}

str2rgb = function(rgb) {
  let sep = rgb.indexOf(",") > -1 ? "," : " ";
  // Turn "rgb(r,g,b)" into [r,g,b]
  rgb = rgb.substr(4).split(")")[0].split(sep)
  return { r: rgb[0], g: rgb[1], b: rgb[2] }
}

getContrastRatio = function(c1, c2) {
  c1 = str2rgb(c1)
  c2 = str2rgb(c2)
  let l1 = getLuminance(c1.r, c1.g, c1.b);
  let l2 = getLuminance(c2.r, c2.g, c2.b);

  return (Math.max(l1, l2) + 0.05) / (Math.min(l1, l2) + 0.05);
}

getColorValues = function(el) {
  return {
    fg: window.getComputedStyle(el).getPropertyValue('color'),
    bg: window.getComputedStyle(el).getPropertyValue('background-color')
  }
}

formatContrastRatio = function(el) {
  const {fg, bg} = getColorValues(el)
  let ratio = getContrastRatio(fg, bg)
  ratio = Math.round(ratio * 100) / 100
  let status = '&#x2714;'
  if (ratio < 4.5) status = '&#x203C;'
  if (ratio < 3) status = '&#x274C;'
  return `${status} ${ratio}`
}

formatContrastRatioLink = function(el) {
  const {fg, bg} = getColorValues(el)
  return 'https://contrast-ratio.com/#' + 
    encodeURIComponent(`${fg}-on-${bg}`)
}
```

> All of R's [named colors](https://rdrr.io/r/grDevices/colors.html)
> in [one CSS stylesheet](dist/r-colors.css).


```{r child="usage.Rmd"}
```


## Colors

:::::: {.color-picker}

<div id="demo-text" class="bg-white black"><h2>Preview</h2><p>Click on a color below</p><a id="demo-contrast" title="WCAG Contrast Ratio" href='#' target="_blank" rel="noopener"></a></div>

::: {.table-responsive .h-100 .overflow-hidden} :::

```{r echo=FALSE}
library(glue)
r_colors <- readRDS("r_colors.rds")

x <- data.frame(
  name = glue('<span class="foreground {r_colors$name}">{r_colors$name}</span>'),
  color = glue('<span class="background bg-{r_colors$name}"></span>'),
  rgb = r_colors$color,
  hex = r_colors$hex,
  colorName = r_colors$name
)
```

```{r echo=FALSE}
reactable::reactable(
  data = x,
  sortable = TRUE,
  searchable = TRUE,
  pagination = FALSE,
  highlight = TRUE,
  height = "100%",
  columns = list(
    name = reactable::colDef("Name", html = TRUE),
    color = reactable::colDef("Color", html = TRUE),
    rgb = reactable::colDef("RGB Value"),
    hex = reactable::colDef("Hex Value"),
    colorName = reactable::colDef(show = FALSE)
  ),
  defaultColDef = reactable::colDef(minWidth = 185),
  onClick = reactable::JS("
    function(rowInfo, colInfo) {
      if (!['name', 'color'].includes(colInfo.id)) return
      
      const preview = document.getElementById('demo-text')
      const contrast = document.getElementById('demo-contrast')
      
      const classCell = colInfo.id === 'name' ? 'foreground' : 'background'
      let fg = [...preview.classList].filter(x => !/^bg-/.test(x))
      let bg = [...preview.classList].filter(x => /^bg-/.test(x))
      debugger;
      if (classCell == 'foreground') {
        fg = rowInfo.row.colorName
      } else {
        bg = 'bg-' + rowInfo.row.colorName
      }
      
      preview.classList = fg + ' ' + bg
      preview.querySelector('p').innerHTML = 
        `The quick brown fox jumps over the lazy dog.<br><br>
        <span class=\"mono\">class=\"${fg} ${bg}\"</span>`
      
      let hoverClasses = preview.classList.toString().split(' ').map(s => s + '-hover')
      hoverClasses[0] = 'bg-' + hoverClasses[0]
      hoverClasses[1] = hoverClasses[1].replace('bg-', '')
      contrast.classList = preview.classList + ' ' + hoverClasses.join(' ')
      
      setTimeout(function() {
        contrast.innerHTML = formatContrastRatio(preview)
        contrast.href = formatContrastRatioLink(preview)
      }, 200)
    }
  ")
)
```


:::

::::::

<div id="toggle-dark-mode"></div>

```{js, echo=FALSE}
const toggleDarkMode = document.getElementById('toggle-dark-mode')
toggleDarkMode.addEventListener('click', function() {
  document.body.classList.toggle('darkmode')
})
```

<a href="https://github.com/gadenbuie/r-colors-css" class="github-corner" aria-label="View source on GitHub"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:var(--darkorange1); color:#fff; position: fixed; top: 0; border: 0; right: 0; z-index:1001;" aria-hidden="true"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>
