## Usage

For modularity, there are several stylesheets available.
If you just want foreground and background colors,
[download `r-colors.css`](dist/r-colors.css)

```r
download.file(
  "https://pkg.garrickadenbuie.com/r-colors-css/dist/r-colors.css",
  "r-colors.css"
)
```

and then add it to your HTML R Markdown documents

````markdown
output: 
  html_document:
    css: r-colors.css
````

or your [xaringan](https://slides.yihui.org/xaringan) slides

````markdown
output: 
  xaringan::moon_reader:
    css: r-colors.css
````

or just about anywhere else

```{r eval=FALSE}
htmltools::includeCSS("r-colors.css")
```

```{r echo=FALSE}
set.seed(44)
demo_color <- sample(colors(), 1)
```


Each of the 
`r format(length(colors()), big.mark = ',')` colors 
are available in few ways,
using the color name.
For example, 
the R color named
`"`r demo_color`"`
is available

1. as a **foreground** color-setting class: <code>.`r demo_color`</code>

1. as a **background** color-setting class: <code>.bg-`r demo_color`</code>

1. [r-colors.vars.css](dist/r-colors.vars.css) provides each color
   as a [css variable](https://developer.mozilla.org/en-US/docs/Web/CSS/--*): `var(--`r demo_color`)`
   
1. [r-colors.hover.css](dist/r-colors.hover.css) provides each color
   as a foreground or background color-on-hover class:
   `.`r demo_color`-hover` or `.bg-`r demo_color`-hover`
